Pangenome graph layout by HOGWILD! path-guided stochastic gradient descent

### 2022-09-21 manuscript/main.tex
update affiliations

\author{ %[Heumos, \textit{et~al}.]{
  Simon Heumos\,$^{1,2 \dagger}$,
  Andrea Guarracino\,$^{3 \dagger}$,
  Jan-Niklas Manuel Schmelzle\,$^{4,5}$,
  Jiajie Li\,$^{4,5}$,
  Zhiru Zhang\,$^{5}$,
  Sven Nahnsen\,$^{1,2}$,
  Pjotr Prins\,$^6$,
  and Erik Garrison\,$^{6 *}$
}

>>>>

\author{ %[Heumos, \textit{et~al}.]{
  Simon Heumos\,$^{1,2 \dagger}$,
  Andrea Guarracino\,$^{3 \dagger}$,
  Jan-Niklas Manuel Schmelzle\,$^{4,5}$,
  Jiajie Li\,$^{5}$,
  Zhiru Zhang\,$^{5}$,
  Sven Nahnsen\,$^{1,2}$,
  Pjotr Prins\,$^6$,
  and Erik Garrison\,$^{6 *}$
}
